SAT Competition 2020\tnoteref{title}

### 2021-06-04 paper/main.tex
ipasir

As can be seen in Table~\ref{tab:families}, $27$ authors contributed a set of $1260$ previously unseen benchmark instances from
a wide range of different instance families. 
In order to compile a balanced set of $300$ benchmark instances, we first removed  instances solved by \solver{Minisat} in less than $10$ minutes, thus obtaining a reduced set of $1012$ instances. 
We considered a maximum of $14$ submissions per author using a procedure detailed as Algorithm~\ref{algo:select}. 
Per author, if possible, we first randomly selected $7$ satisfiable and $7$ unsatisfiable instances (Lines~3 and~4). 
If this did not yield a total of $14$ instances, we added instances of yet unknown result (Lines~5--7). 
Of the such obtained $308$ instances, we randomly removed $8$ satisfiable instances, yielding a total of $114$ satisfiable, $78$ unsatisfiable and $108$ instances of unknown result.

To obtain the final compilation of $400$ benchmark instances, we augmented this set with $100$ instances which have been used in previous competitions. 
We randomly selected $21$ satisfiable, $57$ unsatisfiable and $22$ unknown instances to yield a total of $135$ satisfiable, $135$ unsatisfiable, and $130$ instances of unknown result. 
Furthermore, we made sure not to select instances of families which are already represented in the set of newly submitted instances and moreover excluded random, agile and planning instances (due to the Planning track).

@@

The Incremental Library track was introduced in SAT~Race~2015~\cite{Balyo:2015:SATRace} and also took place in SAT~Competitions 2016 and 2017.
Benchmarks for the Incremental Library track consist of \emph{benchmark applications} which implement and use the incremental SAT solver in their back-end as well as \emph{benchmark instances} which serve as input to these applications. 
For evaluating the Incremental Library track, we used six applications which implement the IPASIR interface, ranging from determination of backbone variables to SAT-based planning. 
For each of those applications, we individually selected $50$ problem instances serving as input for the respective application.

@@

@@

Many prominent applications of SAT use an \emph{incremental} SAT solver in their back-end. 
Those incremental use-cases impose additional challenges on solver authors. 
The emergence of new fuzzing tools for incremental SAT solvers based on IPASIR can help researchers with also integrating and testing their methods in the incremental use-case.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}

>>>>

As can be seen in Table~\ref{tab:families}, $27$ authors contributed a set of $1260$ previously unseen benchmark instances from a wide range of different instance families. 
In order to create a balanced set of 300 new benchmarks and 100 old benchmarks, i.e., instances seen in previous competitions, we executed the following steps of \emph{rule-based randomization}.

To compile the set of 300 new instances, we first applied a hardness criterion by filtering out all instances solved by \solver{Minisat} in less than 10 minutes. 
From the resulting 1012 instances, we randomly selected $k$ instances per author, with a minimum $k$ such that the result set contains at least 300 instances.
Algorithm~\ref{algo:select} depicts the details. 
We randomly selected $7$ satisfiable and $7$ unsatisfiable instances per author (Lines~3 and~4) and added instances of yet unknown result if this did not yield a total of $14$ instances (Lines~5--7). 
Of the such obtained $308$ instances, we randomly removed $8$ satisfiable instances, yielding a total of $114$ satisfiable, $78$ unsatisfiable and $108$ instances of unknown result.

We augmented this set with $100$ instances from previous competitions as follows. 
In order to further balance the amount of satisfiable and unsatisfiable instances in the new benchmark set, we randomly selected $21$ satisfiable, $57$ unsatisfiable and $22$ unknown instances. 
With additional constraints, we made sure not to select instances of families which are already represented in the set of 300 new instances (cf. Table~\ref{tab:families}). 
We also excluded random, agile and planning instances (due to the Planning track). 
The final selection of benchmark instances contains $135$ satisfiable, $135$ unsatisfiable, and $130$ instances of unknown result (cf.~Table~\ref{tab:final}).

@@

The Incremental Library track was introduced in SAT~Race~2015~\cite{Balyo:2015:SATRace} and also took place in SAT~Competitions 2016 and 2017.
Benchmarks for the Incremental Library track consist of \emph{benchmark applications} which implement and use the incremental SAT solver in their back-end as well as \emph{benchmark instances} which serve as input to these applications. 
For evaluating the Incremental Library track, we used six available IPASIR applications, ranging from determination of backbone variables to SAT-based planning. 
For each application, we individually selected 50 application instances as follows.

@@

In the instance selection, the author-wise balancing of satisfiable and unsatisfiable instances was often counter-productive and did not lead to a more balanced overall selection of new instances. 
Moreover, this practice discriminated against authors of purely satisfiable or unsatifiable sets of instances. 
Also the hardness criterion of 10 \solver{Minisat} minutes was higher than the hardness criterion of 1 \solver{Minisat} minute of the BYOB rule. 
In future competitions, we will not balance by \emph{satisfiablity} on the author level, we will be more consistent or clear with our \emph{hardness} criteria, and we will specify what it means for an instance to be counted as \emph{unknown}.

The IPASIR interface facilitates the integration of SAT Solvers into incremental applications. 
In contrast to benchmarking with instances given in DIMACS CNF, there are only a couple of benchmark applications available for the Incremental track which are also less organized. 
This calls for the creation of a more diverse and organized repository of applications for incremental SAT solvers. 
Proper benchmarking and new tools for testing incremental SAT solvers can help solver authors to deal with the more complex use-case.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}

@@
